### 2016-11-01 ms/ms.tex
communities figure
added cover letter

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turned
  over at higher rates in assembling hedgerows as the networks
  continually reorganized. Nestedness of assembling networks also
  increased through time, but there was no increase in robustness to
  simulated plant extinctions. The sensitivity of networks to
  cascading perturbations, however, increased as the communities
  assembled, at least partially due to accumulating species
  richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem service? provision in
  agricultural areas.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by module. The bottom panels visualize
    the flow of species between modules between changing points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage

>>>>

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turned
  over at higher rates in assembling hedgerows as the networks
  continually reorganized. Nestedness of assembling networks also
  increased through time, but there was no increase in robustness to
  simulated plant extinctions. The sensitivity of networks to
  cascading perturbations, however, increased as the communities
  assembled, at least partially due to accumulating species
  richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation provision in agricultural areas.
\end{abstract}

@@

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by module. The bottom panels visualize
    the flow of species between modules between changing points. }
  \label{fig:changePoints2}
\end{sidewaysfigure}
\clearpage
